%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=blue,
}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Shounak Shastri}
   & \href{https://shounakshastri.github.io}{https://shounakshastri.github.io}\\
  Email : \href{mailto: shounak.shastri@gmail.com}{shounak.shastri@gmail.com}
  & \href{https://www.linkedin.com/in/shounak-shastri/}{https://www.linkedin.com/in/shounak-shastri/}\\
  Mobile : (+91) 86809 31795 & Address: 2 - Shankar Nagar, Nagpur - 440010\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Vellore, TN, India}
      {Doctorate (Ph.D.) in Steganography Algorithms}{Jun.2015 -- Dec. 2020}
     \resumeSubheading
      {Vellore Institute of Technology}{Vellore, TN, India}
      {Master of Technology (M.Tech.) in Communication Engineering}{Jun.2013 -- May. 2015}
    \resumeSubheading
      {K. J. Somaiya College of Engineering}{Mumbai, MH, India}
      {Bachelor of Engineering (B.E.) in Electronics Engineering}{Aug. 2007 -- July. 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {VIT--Vellore}{Vellore, TN, IN}
      {Teaching cum Research Assistant (4 years)}{Jan. 2016 -- Jan. 2020}
      \resumeItemListStart
        \resumeItem{Teaching}
          {TensorFlow is an open source software library for numerical computation using data flow graphs; primarily used for training deep learning models. Worked on APIs and performance for training models on Tensor Processing Units (TPU).}
        \resumeItem{Research}
          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines, as well as a set of language-specific SDKs for constructing pipelines and runners.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Dual Image RDH with Trinary Encoding}
      {Devised a dual image steganography algorithm using a novel encoding technique called Trinary Encoding. Published in peer-reviewed international journal with Impact Factor 2.479.}
    \resumeSubItem{PEE based Dual Image RDH}
      {Modified the common PEE scheme to fit the Dual Image Steganography scenario. Resulted in an 100\% increase in the Embedding Capacity. Presented and published in IEEE International Conference.}
    \resumeSubItem{Word Predictor (NLP)}
      {Implemented a n-gram word predictor in R.} \href{link}{https://shounakshastri.github.io/blogposts/}\\
    \resumeSubItem{Browser Based Object Classification}
      {Developed browser based object classification using TensorflowJS. Used Transfer Learning to train a MobileNet Neural Network}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Programming Languages}{: Python, R, Matlab}}
    \item{
      \textbf{Technologies}{: OpenCV, Numpy, Scipy, Tensorflow, Scikit Learn, NLTK, Matplotlib, Trax}
    }
  \resumeSubHeadingListEnd

%---------Publications and Awards-------
\section{Publications and Awards}
	\resumeSubHeadingListStart
		\resumeSubheading
			{Research Awards}{VIT - Vellore, TN, IN}
			{}{2016, 2017}
			
			{Awarded for research work carried out on Steganography algorithms.}
		\resumeSubheading{Best Paper Award}{VITEEE}{IEEE International Conference, Vellore}{2019}
		\resumeSubheading{Journal Publications}{}{}{}
			\resumeItemListStart
				\resumeItem{}{S. Shastri and V. Thanikaiselvan, “Dual image reversible data hiding using trinary assignment and centre folding strategy with low distortion,” J. Vis. Commun. Image Represent., vol. 61, pp. 130–140, May 2019. DOI: https://doi.org/10.1016/j.jvcir.2019.03.022
					}
				\resumeItem{}{V. Thanikaiselvan, S. Shastri, and S. Ahmad, “Information hiding: Steganography,” Stud. Comput. Intell., vol. 660, pp. 65–91, 2017. DOI: https://doi.org/10.1007/978-3-319-44790-2\_4}
				\resumeItem{}{S. Shastri and V. Thanikaiselvan, “PVO based Reversible Data Hiding with improved embedding capacity and security,” Indian J. Sci. Technol., vol. 9, no. 5, 2016.
				}
			\resumeItemListEnd

	\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
